Distinction Centrality Analysis

### 2025-09-07 analysis.qmd
new toys

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(patchwork)
   library(dplyr)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "plot.graph.norm.R"))
```

@@

```{r Toy Examples}
   source(here("Functions", "distinction.R"))
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- g1 + edge(2,3)
   g10 <- g10 + edge(3,4)
   g10 <- g10 + edge(4,5)
   g10 <- g10 + edge(5,6)
   g10 <- g10 + edge(6,7)
   g10 <- g10 + edge(7,2) #wheel graph
   g11 <- make_ring(8) 
   g11 <- delete_vertices(g11, 8) #path graph
```

```{r Bonacich examples}
   g13 <- make_empty_graph(10, directed = FALSE)
   g13 <- g13 + edge(1,2)
   g13 <- g13 + edge(1,3)
   g13 <- g13 + edge(1,9)
   g13 <- g13 + edge(2,3)
   g13 <- g13 + edge(2,10)
   g13 <- g13 + edge(3,4)
   g13 <- g13 + edge(4,5)
   g13 <- g13 + edge(4,6)
   g13 <- g13 + edge(5,10)
   g13 <- g13 + edge(5,6)
   g13 <- g13 + edge(6,7)
   g13 <- g13 + edge(7,8)
   g13 <- g13 + edge(7,9)
   g13 <- g13 + edge(8,10)
   g13 <- g13 + edge(8,9) #Bonacich (2007) regular network Fig. 5
   g14 <- make_empty_graph(12, directed = FALSE)
   g14 <- g14 + edge(1,2)
   g14 <- g14 + edge(1,6)
   g14 <- g14 + edge(1,7)
   g14 <- g14 + edge(2,3)
   g14 <- g14 + edge(2,10)
   g14 <- g14 + edge(3,4)
   g14 <- g14 + edge(3,8)
   g14 <- g14 + edge(4,5)
   g14 <- g14 + edge(4,11)
   g14 <- g14 + edge(5,6)
   g14 <- g14 + edge(5,9)
   g14 <- g14 + edge(6,12)
   g14 <- g14 + edge(7,8)
   g14 <- g14 + edge(7,9)
   g14 <- g14 + edge(8,9)
   g14 <- g14 + edge(10,11)
   g14 <- g14 + edge(10,12)
   g14 <- g14 + edge(11,12)
```

```{r Estrada examples}
   g15 <- make_empty_graph(8, directed = FALSE)
   g15 <- g15 + edge(1,2)
   g15 <- g15 + edge(1,5)
   g15 <- g15 + edge(1,8)
   g15 <- g15 + edge(2,3)
   g15 <- g15 + edge(2,8)
   g15 <- g15 + edge(3,4)
   g15 <- g15 + edge(3,6)
   g15 <- g15 + edge(4,5)
   g15 <- g15 + edge(4,7)
   g15 <- g15 + edge(5,6)
   g15 <- g15 + edge(6,7)
   g15 <- g15 + edge(7,8) #Fig 1(a) https://doi.org/10.1103/PhysRevE.71.056103
   g16 <- make_full_graph(9, directed = FALSE)
   g16 <- g16 - edge("1|6")
   g16 <- g16 - edge("1|5")
   g16 <- g16 - edge("2|4")
   g16 <- g16 - edge("2|9")
   g16 <- g16 - edge("3|6")
   g16 <- g16 - edge("3|8")
   g16 <- g16 - edge("4|7")
   g16 <- g16 - edge("5|8")
   g16 <- g16 - edge("7|9") #Fig 1(b) https://doi.org/10.1103/PhysRevE.71.056103
```

```{r Toy Networks Plots}
   source(here("Functions", "distinction.R"))
   source(here("Functions", "plot.graph.norm.R"))
   png(here("Plots", "Toys", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-triangle.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-long.png"))
   plot.graph.norm(g7, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "clique.png"))
   plot.graph.norm(g8, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "kite.png"))
   plot.graph.norm(g9, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "wheel.png"))
   plot.graph.norm(g10, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "path.png"))
   plot.graph.norm(g11, l = "kk")
   dev.off()
   source(here("Functions", "plot.graph.cat.R"))
   png(here("Plots", "Toys", "bonacich1.png"))
   plot.graph.cat(g13, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "bonacich2.png"))
   plot.graph.cat(g14, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "estrada1.png"))
   plot.graph.cat(g15, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "estrada2.png"))
   plot.graph.cat(g16, l = "circle")
   dev.off()
```

@@

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(patchwork)
   library(dplyr)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "plot.graph.norm.R"))
   plot.toys <- function(x, n, l) {
      ggsave(here("Plots", "Toys", n), 
         plot = plot.graph.norm(x, l = l)
         )
      }
   del.names <- function(x) {
      return(delete_vertex_attr(x, "name"))
      }
```

@@

```{r Building Blocks}
   c3 <- make_full_graph(3, directed = FALSE) # triangle
   c4 <- make_full_graph(4, directed = FALSE) # 4-clique
   c5 <- make_full_graph(5, directed = FALSE) # 5-clique
   t3 <- make_tree(n = 4, children = 3, mode = "undirected") # 3-tree
   t2 <- make_tree(n = 3, children = 2, mode = "undirected") # 2-tree
```

```{r Basic Toy Graphs}
   s7 <- make_star(7, mode = "undirected") # 7-star graph
   plot.toys(s7, "star.png", "kk")
   c7 <- make_full_graph(7, directed = FALSE) # 7-clique
   plot.toys(c7, "clique.png", "circle")
   r7 <- make_ring(7) # 7-circle graph
   plot.toys(r7, "circle.png", "circle")
   c6 <- make_full_graph(6, directed = FALSE) # 6-clique
   k7 <- add_vertices(c6, 1) # 6-clique plus node
   k7 <- k7 + edge(1,7) # 7-kite
   plot.toys(k7, "kite.png", "kk")
   r6 <- make_ring(6) # 6-circle graph
   V(r6)$name <- as.character(2:7)
   V(s7)$name <- as.character(1:7)
   w7 <- s7 + r6 # 7-wheel-graph
   r6 <- del.names(r6)
   s7 <- del.names(s7)
   w7 <- del.names(w7)
   plot.toys(w7, "wheel.png", "kk")
   r8 <- make_ring(8) # 8-circle graph
   p7 <- delete_vertices(r8, 8) #path graph
   plot.toys(p7, "path.png", "kk")
```

```{r Mediator versus Weld}
   c1 <- c4
   c2 <- c4
   V(c1)$name <- as.character(1:4)
   V(c2)$name <- as.character(4:7)
   sf4 <- c1 + c2  # structural fold four-clique
   sf4 <- del.names(sf4)
   plot.toys(sf4, "sf4.png", "kk")
   c1 <- c5
   c2 <- c5
   V(c1)$name <- as.character(1:5)
   V(c2)$name <- as.character(5:9)
   sf5 <- c1 + c2  # structural fold five-clique
   sf5 <- del.names(sf5)
   plot.toys(sf5, "sf5.png", "kk")
   b3 <- c3 + c3
   b3 <- add_vertices(b3, 1)
   b3 <- b3 + edge(7,1)
   b3 <- b3 + edge(7,4) # broker between triangles
   plot.toys(b3, "broker3.png", "kk")
   b4 <- c4 + c4
   b4 <- add_vertices(b4, 1)
   b4 <- b4 + edge(9,1)
   b4 <- b4 + edge(9,5) # broker between four-cliques
   plot.toys(b4, "broker4.png", "kk")
```

```{r Triadic Closure}
   ct <- r7 + edge(6,1) # circle graph plus triangle
   plot.toys(ct, "circle-triangle1.png", "circle")
   cl <- r7 + edge(7,4) # circle graph plus long tie
   plot.toys(cl, "circle-long.png", "circle")
   st1 <- s7 + edge(2,3) # star graph plus one triangle
   plot.toys(st1, "start-triangle1.png", "kk")
   st2 <- st1 + edge(5,6) # star graph plus two triangles
   plot.toys(st2, "start-triangle2.png", "kk")
```

```{r Mediator Parameters}
   t222 <- t2 + t2
   t222 <- add_vertices(t222, 1)
   t222 <- t222 + edge(7, 1)
   t222 <- t222 + edge(7, 4) # tree mediator two branch
   plot.toys(t222, "tree-mediator2.png", "kk")
   t232 <- t3 + t3
   t232 <- add_vertices(t232, 1)
   t232 <- t232 + edge(9, 1)
   t232 <- t232 + edge(9, 5) # tree mediator three branch
   plot.toys(t232, "tree-mediator3.png", "kk")
   t222l <- t222 + edge(6, 2) # tree mediator two branch plus long
   plot.toys(t222l, "tree-mediator2-long.png", "auto")
   t232l <- t232 + edge(7, 2) # tree mediator three branch plus long
   plot.toys(t232l, "tree-mediator3-long.png", "auto")
```
```{r Mediator Parameters}
   c1 <- make_ring(4)
   c2 <- make_ring(4)
   V(c1)$name <- as.character(1:4)
   V(c2)$name <- as.character(4:7)
   cw <- c1 + c2  # circle weld
   tc <- cw + edge(2, 4)
   tc <- tc + edge(4, 6) # two-connected
   tcl <- tc + edge(1, 7) # two-connected plus long tie
   cw <- del.names(cw)
   tc <- del.names(tc)
   tcl <- del.names(tcl)
   plot.toys(cw, "circle-weld.png", "auto")
   plot.toys(tc, "two-connected.png", "kk")
   plot.toys(tcl, "two-connected-long.png", "kk")

```

@@

```{r}
   library(networkdata)
   distinction(karate, norm = "max")
   plot.graph.norm(karate)
```
